---
title: 'Severe weather events: economic and health impacts'
author: "Vv"
date: "04/24/2015"
output: html_document
---


###Synopsis


###Data Processing
Note: current stable version of 'data.table' library, 1.9.4, is not able to read dataset being vivisected. So, to make it work, you should update data.table to v1.9.5 or higher, as described [here](https://github.com/Rdatatable/data.table/wiki/Installation). In short: 

    # To install development version
    library(devtools)
    install_github("Rdatatable/data.table", build_vignettes = FALSE)

    # If you would like to revert back to CRAN version
    remove.packages("data.table")         # First remove the current version
    install.packages("data.table")        # Then install the CRAN version

Latest commit at the time of writing of this paper is 6601aab68559308654ab6dad7e2181f510a44b1f.

```{r setoptions,echo=TRUE}
library(data.table);
if (!exists("rawData")){
    rawData <- fread("repdata-data-StormData.csv", stringsAsFactors = FALSE, sep = ",", header = TRUE);
}
```

here are the data from the point of bird’s-eye view:

```{r}
str(rawData)
```



###Results

For the purposes of this report PROPDMGEXP has been treated as...

